---
title: "Form of ISDs, IEDs workflow"
output: html_notebook
---
# Setup, get data
```{r setup, get community data}
library(neonbecs)
dat <- get_toy_portal_data()

head(dat)

dat_energy <- dat %>%
  replicatebecs::add_energy_sizeclass()

dat_isd <- dat_energy %>%
  make_isd()

head(dat_isd)

```

## Plot data

```{r plot data}

ied_plot <- plot_ied(ied = dat_isd, ied_name = "Toy Portal")

isd_plot <- plot_isd(isd = dat_isd, isd_name = "Toy Portal")

dat_bsd <- replicatebecs::make_bsd(raw_community = dat, ln_units = .1)
bsd_plot <- replicatebecs::plot_bsd(bsd = dat_bsd, bsd_name = "Toy Portal")
print(ied_plot)
print(isd_plot)
print(bsd_plot)
```

# Fitting & plotting distributions

## Powerlaw

### Fit powerlaw

```{r fit power law}
pl_par_size <- get_pl_pars(dat = dat, estimate_min = TRUE, size_or_energy = "size")

pl_size_sample <- sample_pl(dat = dat, plpars = pl_par_size, nsamples = 1000)

pl_par_size_forcemin <-  get_pl_pars(dat = dat, estimate_min = FALSE, size_or_energy = "size")

pl_size_forcemin_sample <- sample_pl(dat = dat, plpars = pl_par_size_forcemin, nsamples = 1000)
```

### Plot power law

```{r plot a sample from fitted pl}
pl_isd <- dat %>%
  dplyr::mutate(individual_sizes = pl_size_sample[,1]) %>%
  replicatebecs::add_energy_sizeclass() %>%
  make_isd()

pl_isd_plot <- plot_isd(pl_isd, isd_name = "Sampled power law")

print(pl_isd_plot)

pl_isd_fm <- dat %>%
  dplyr::mutate(individual_sizes = pl_size_forcemin_sample[,1]) %>%
  replicatebecs::add_energy_sizeclass() %>%
  make_isd()

pl_isd_fm_plot <- plot_isd(pl_isd_fm, isd_name = "Sampled power law forced min")

print(pl_isd_fm_plot)

```

### Bootstrap power law

RMD is puzzled re: whether it makes sense to bootstrap logliks from powerlaw

OR 

do some kind of subsetting data into training and test datasets and then seeing how well the power law can predict data in the test dataset.

This seems like more of a formality than anything, these are visually *not* well described by these power law fits.

```{r bootstrap power laws}
pl_loglik_sampled <- apply(pl_size_sample, MARGIN = 2, FUN = loglik_pl, plpars = pl_par_size)
pl_loglik_sampled_emp <- loglik_pl(dat$individual_sizes, plpars = pl_par_size)
pl_loglik_sampled_ecdf <- ecdf(pl_loglik_sampled)
pl_loglik_size_z <- pl_loglik_sampled_ecdf(pl_loglik_sampled_emp)

pl_loglik_sampled_forcemin <- apply(pl_size_forcemin_sample, MARGIN = 2, FUN = loglik_pl, plpars = pl_par_size_forcemin)
pl_loglik_fm_sampled_emp <- loglik_pl(dat$individual_sizes, plpars = pl_par_size_forcemin)
pl_loglik_fm_sampled_ecdf <- ecdf(pl_loglik_sampled_forcemin)
pl_loglik_size_fm_z <- pl_loglik_fm_sampled_ecdf(pl_loglik_fm_sampled_emp)


pl_loglik_size_z
pl_loglik_size_fm_z
```

## GMM

### Fit GMM

```{r fit GMM}
dat_gmm <- fit_gmm(dat_isd)
dat_gmm_pdf <- get_pdf(dat_gmm)
```

### Plot GMM

```{r plot GMM}
gmm_plot <- plot_gmm_pdf(dat_gmm_pdf, pdf_name = "Toy Portal")
print(gmm_plot)
```

### Bootstrap GMM?
